Technical Report

### 2018-03-21 fully-abstract-comp/technical-report.tex
Remove some outdated notes.

\section{Notes}
\subsection{Leuven stay conclusions}
\begin{enumerate}
\item Enter capabilities replaces by sealed code/data pairs \label{item:first-point}
  \begin{itemize}
  \item To allow us to forbid dynamic code generation
  \end{itemize}
\item Conditional full-abstraction
  \begin{itemize}
  \item No undefined behaviour by \emph{trusted code} in any context implies full-abstraction. (Blame idea: undefined as undef of current pc, so current pc can be checked for whether it was the trusted code).
  \item Avoids dynamic checks to protect trusted code against itself.
  \item Possible due to point \ref{item:first-point}.
  \end{itemize}
\item replace push/pull/call/ret/sload by symbolic return pointer (pair) and stack pointer.
  \begin{itemize}
  \item Allows back translation to be embedding into source language.
    \begin{itemize}
    \item Interpreter for back translation is not able to accurately replicate code length.
    \end{itemize}
  \end{itemize}
\item Worlds similar to CSF paper, but invariants on seals as well.
  \begin{itemize}
  \item Invariants says what can be sealed with a certain seals.
  \end{itemize}
\item Linker: resolves symbols
  \begin{itemize}
  \item Export refs (Question: do we allow other things than sealed code/data pairs to be exported?)
  \item Import refs
  \item Fresh seal requirement
  \end{itemize}
\item Components are memory segments and symbols.
\item Variable instruction length in the source to avoid leaking information through code size that cannot be matched after compilation (breaks compiler correctness, see example in subsection~\ref{subsec:capability-opacity}).
  \begin{itemize}
  \item Notice x86 allows instructions of up to infinite length, so this is not weird.
  \end{itemize}
\item Have opaque capabilities.
  \begin{itemize}
  \item Without opaque capabilities, stack consumption could be inferred through stack pointer index etc.
  \end{itemize}
\item Considered PORs for transition systems to: ($a \rightarrow b \Rightarrow a \rightarrow a \text{ and } b \rightarrow b$)
  \dominique{27-09-2017: I don't remember what we meant with PORs, but perhaps quasi-reflexive partial orders.  Not sure what the point of this was again... }
  \lau{28-09-2017: I think the next three points is the answer. We basically wanted a formalism in which we could design one region that would govern the stack. I do not remember why it was made possible with PORs.}
  \begin{itemize}
  \item Define one region that governs the stack
  \item Make the regions more general
  \item For now, we have not done this: instead we stick with the transition systems we have and have two regions governing the stack reflecting the CSF work.
  \end{itemize}
\end{enumerate}

>>>>

\section{Notes}
\subsection{Leuven stay conclusions}
\begin{enumerate}
\item Enter capabilities replaced by sealed code/data pairs \label{item:first-point}
  \begin{itemize}
  \item To allow us to forbid dynamic code generation
  \end{itemize}
\item Conditional full-abstraction
  \begin{itemize}
  \item No undefined behaviour by \emph{trusted code} in any context implies full-abstraction. (Blame idea: undefined as undef of current pc, so current pc can be checked for whether it was the trusted code).
  \item Avoids dynamic checks to protect trusted code against itself.
  \item Possible due to point \ref{item:first-point}.
  \end{itemize}
\item replace push/pull/call/ret/sload by symbolic return pointer (pair) and stack pointer.
  \begin{itemize}
  \item Allows back translation to be embedding into source language.
    \begin{itemize}
    \item Interpreter for back translation is not able to accurately replicate code length.
    \end{itemize}
  \end{itemize}
\item Worlds similar to CSF paper, but invariants on seals as well.
  \begin{itemize}
  \item Invariants says what can be sealed with a certain seals.
  \end{itemize}
\item Linker: resolves symbols
  \begin{itemize}
  \item Export refs (Question: do we allow other things than sealed code/data pairs to be exported?)
  \item Import refs
  \item Fresh seal requirement
  \end{itemize}
\end{enumerate}
